Specialisation \& the Latitude-niche-breadth Hypothesis

### 2015-10-12 talk/ABC_2015.tex
Ok this will do for the test talk

      Want to show a dummy negative Gen vs. Lat due to S

@@

      \begin{columns}
        \column{.5in}
        \column{2in}

@@

        \includegraphics[width=.8\columnwidth]{Figures/spring_stream.eps}

@@

        \includegraphics[width=.8\columnwidth]{Figures/fall_stream.eps}

        \column{2in}

      \end{columns}
    \end{block}
  \end{frame}

  \begin{frame}{What's different in freshwaters?}
    \begin{block}{They're highly seasonal - except in NZ}
      [same pics]
    \end{block}
  \end{frame}

  % Heading off the "but so are terrestrial" issue
  \begin{frame}{What's different in freshwaters?}
    \begin{block}{They're aquatic}

      [picture of a fish vs. a land beast]
      [gape limitation]

    \end{block}
  \end{frame}

\section*{Conclusion and Acknowledgements}
  \begin{frame}{So why are there more species in the tropics?}
    \begin{block}{Estuarine, marine, \& terrestrial}
      \begin{itemize}
        \item Broader niche space in the tropics
        \item Similar specialisation everywhere
      \end{itemize}
    \end{block}

    \begin{block}{Lakes \& Streams}
      \begin{itemize}
        \item Narrower niches in the tropics
        \item Generality due to seasonality?
      \end{itemize}
    \end{block}
  \end{frame}

@@

      \column{.25in}
    \end{columns}
    \begin{columns}
     \column{2.5in}
       \centering

      \vspace{.25cm}

       \includegraphics[width=0.6\columnwidth]{marsden-logo-cmyk-tif.eps}

      \vspace{.25cm}

      \includegraphics[width=0.7\columnwidth]{Dal_logo.eps}

     \column{2.5in}
       \centering

      \vspace{.25cm}

       \includegraphics[width=0.7\columnwidth]{NSERC_C.eps}

       \vspace{.25cm}

       \includegraphics[width=0.4\columnwidth]{logo-canterbury-color.eps}

       \vspace{.5in}

    \end{columns}
  \end{frame}

  \begin{frame}{Latitude affects scaling - sometimes}

  [Show the 5-panel plot, the equation.]

>>>>

    \begin{center}
      \includegraphics*[width=.654\textwidth]{Figures/results/Gen_vs_lat_negative.eps}

    \vspace{.3cm}
      {\color{white}{\Large      
      $G \approx aS^b$}}
    \end{center}

@@

      \begin{columns}
        \column{.5in}
        \column{1.9in}

        \hfill \includegraphics[width=.8\columnwidth]{Figures/spring_stream.eps}

        \vspace{.2in}

        \hfill \includegraphics[width=.8\columnwidth]{Figures/fall_stream.eps}

        \column{.2in}

        \column{1.9in}

        \vspace{.2in}

      \end{columns}
    \end{block}

    \vfill

  \begin{frame}{What's different in freshwaters?}
    \begin{block}{They're highly seasonal - except in NZ}

@@

        \includegraphics[width=3in]{Figures/sawcut.eps}

      \end{center}
    \end{block}
  \end{frame}

  \begin{frame}{What's different in freshwaters?}
    \begin{block}{They're dominated by fish}

      \begin{columns}
      \column{.5in}
      \column{1.9in}
        \hfill
        \includegraphics[width=.8\columnwidth]{Figures/anteater.eps}
      \column{.2in}
      \column{1.9in}
        \includegraphics[width=.8\columnwidth]{Figures/trout.eps}
      \column{.5in}
      \end{columns}
    \end{block}

    \vfill

\section*{Conclusion and Acknowledgements}
  \begin{frame}{So why are there more species in the tropics?}
    \begin{columns}
    \column{.5in}
    \column{2.5in}
      \begin{block}{Estuarine, marine, \& terrestrial}
        \begin{itemize}
          \item Broader niche space\\ in the tropics
          \item Similar specialisation\\ everywhere
        \end{itemize}
      \end{block}

@@

    \begin{block}{Lakes \& Streams}
      \begin{itemize}
        \item Narrower niches\\ in the tropics
        \item Generality due to seasonality?
      \end{itemize}
    \end{block}

      \column{1.5in}
        \centering
        \includegraphics[height=.75in]{Figures/version2.eps}

        \includegraphics[height=.75in]{Figures/version1.eps}
    \column{.5in}
    \end{columns}

@@

      \column{.25in}
    \end{columns}

    \begin{columns}
    \column{.25in}
     \column{2.25in}
       \centering

      \includegraphics[height=.75in]{marsden-logo-cmyk-tif.eps}

      \vspace{.5cm}
      \vspace{.125in}

      \includegraphics[height=.5in]{Dal_logo.eps}

      \vspace{.125in}

     \column{2.25in}
       \centering

       \includegraphics[height=.75in]{NSERC_C.eps}

       \includegraphics[height=.75in]{logo-canterbury-color.eps}

    \column{.25in}
    \end{columns}
  \end{frame}

  \begin{frame}{Latitude affects scaling in freshwaters}

    \begin{columns}
    \column{.5in}
    \column{2.75in}
      \begin{center}
      \includegraphics[height=.8in]{Figures/results/no_effect.eps}
      \end{center}

    \column{.25in}
    \column{1in}
      \begin{center}

        \includegraphics[height=.65in]{Figures/version2.eps}
        \vspace{.3in}

    \column{.5in}
    \end{columns}

    \begin{columns}
    \column{.5in}
    \column{2.75in}
      \begin{center}

      \includegraphics[height=.8in]{Figures/results/effect.eps}
      \end{center}

    \column{.25in}
    \column{1in}
      \begin{center}

        \includegraphics[height=.65in]{Figures/version1.eps}
        \vspace{.3in}

    \column{.5in}
    \end{columns}

    \vspace{.1in}

    {\Large $G \approx aS^{\color{purple}b_0+b_1Latitude+b_2Ecotype+b_3Latitude:Ecotype}$}
